Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-27 main_new.tex
updates

% Determining paths for mobile robotic sensors in order to maximize the
% information gained about an environment is formally known as informative
% path planning. This, and related problems such as the orienteering
% problem \citep{Golden87}, has been studied in the context of graphs,
% where the potential measurement are assigned to nodes on which
% evaluation of different routes can be conducted.
%In this context, a fundamental result from \cite{nemhauser1978analysis} proves that a simple greedy algorithm (iteratively selecting the location which most increases the utility) can achieve a near-optimal solution if the problem can be shown to be \emph{submodular}\footnote{an intuitive diminishing returns property, where the informative value of adding sensors decrease with the number of sensors added.}. Building on this result, \cite{chekuri2005recursive} explored this in the setting of a graph using a recursive greedy algorithm, providing near-optimal solutions depending on the planning horizon and graph resolution. 
Adaptive sampling of an evolving frontal feature has been explored in
\cite{fronts11,Zhang2012,Pinto2018,costa19} using state-based autonomous
agents. These approaches typically use a reactive-adaptive scheme,
whereby exploration does not rely on a statistical model of the
environment, but rather adapts based on closing the sensing and
actuation loop. Myopic sampling, i.e. step-wise selection of the path
(on the graph) which reduces the information criterion the most, has
been used for adaptive surveys \citep{singh2009efficient,Binney2013} which
focus largely on reducing predictive variance or mutual information
(entropy). Because the variance and entropy reduction are independent of
the actual data realizations under the assumption of GP models, the use
of data-driven (adaptive) criteria was introduced to include more
targeted sampling of interesting regions (hotspot sampling) by
\cite{Low2009} and \cite{fossuminformation}.

>>>>

% Determining paths for mobile robotic sensors in order to maximize the
% information gained about an environment is formally known as informative
% path planning. This, and related problems such as the orienteering
% problem \citep{Golden87}, has been studied in the context of graphs,
% where the potential measurement are assigned to nodes on which
% evaluation of different routes can be conducted.
%In this context, a fundamental result from \cite{nemhauser1978analysis} proves that a simple greedy algorithm (iteratively selecting the location which most increases the utility) can achieve a near-optimal solution if the problem can be shown to be \emph{submodular}\footnote{an intuitive diminishing returns property, where the informative value of adding sensors decrease with the number of sensors added.}. Building on this result, \cite{chekuri2005recursive} explored this in the setting of a graph using a recursive greedy algorithm, providing near-optimal solutions depending on the planning horizon and graph resolution. 
Adaptive sampling of an evolving frontal feature has been explored in
\cite{fronts11,Zhang2012,Pinto2018,costa19} using state-based autonomous
agents. These approaches typically use a reactive-adaptive scheme,
whereby exploration does not rely on a statistical model of the
environment, but rather adapts based on closing the sensing and
actuation loop. Myopic sampling, i.e. step-wise selection of the path
(on the graph) which reduces the information criterion the most, has
been used for adaptive surveys \citep{singh2009efficient,Binney2013}
which focus largely on reducing predictive variance or mutual
information (entropy). Because the variance and entropy reduction are
independent of the actual data realizations under the assumption of GP
models, the use of data-driven (adaptive) criteria was introduced to
include more targeted sampling of regions of scientific interest by
\cite{Low2009} and \cite{fossuminformation}.
